\problemname{Matarinnkaup}
\illustration{0.3}{salad}{Image from \href{https://commons.wikimedia.org/wiki/File:Chicken_salad_on_striped_tablecloth.jpg}{commons.wikimedia.org}}

A lot of food and drinks were sold at Nauthóll over the last few days. Now it is time
to take inventory and figure out necessary purchases. This job falls to you.
Given the recipes used at Nauthóll and all receipts from the past few days, how much was
used of each ingredient?

\section*{Input}
The first line of the input contains two integers $1 \leq u, k \leq 10\,000$ where
$u$ is the number of recipes and $k$ is the number of receipts. Next there will be $u$
descriptions of recipes. The first line of each description contains a string giving the
name of the dish. Dish names are unique. The next line contains a single integer $1 \leq h \leq 10\,000$,
the number of ingredients that the recipe calls for. Finally there are $h$ lines, each containing the
name of an ingredient and then an integer $1 \leq x \leq 500$. This means there are $x$ instances of
the ingredient in the dish. Then there will be $k$ descriptions of receipts. Each starts with an integer
$1 \leq n \leq 10\,000$, the number of dishes on the receipt. Then follow $n$ lines, each of them containing
the name of a dish and an integer $1 \leq y \leq 500$. This means that $y$ instances of the dish were
purchased. The names of the dishes will always have appeared in the input above. Each name in the input
is at most $20$ characters and contains only lower case English letters and underscores. The total number
of names in the input will be at most $100\,000$.

\section*{Output}
Print how much is needed of every ingredient, one ingredient per line. On each line the name of the ingredient,
a space and an integer denoting how much is needed should be printed. The ingredients should be printed in
alphabetical order. Underscores are considered to go before all the letters in this order.
If an ingredient isn't needed, it shouldn't be printed.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 50   & There are at most $500$ names in the input. \\ \hline
2     & 50   & No further constraints. \\ \hline
\end{tabular}

