\problemname{Heimilisverk}

\illustration{0.35}{list}{Image from \href{https://www.flickr.com/photos/otacke/12221292503/}{Oliver Tacke}}

Ómar is a very responsible boy and has a list of chores he needs to do. The problem
is that Ómar is very lazy, so the list of unfinished chores has become quite long.
So long, in fact, that he does not remember what chores he has already put on the
list and has thus put duplicates into the list every now and then.

Now he finally intends to do some chores from the list, but he doesn't want to
repeat himself. Can you help him remove duplicate chores from his list? That is
to say, if it appears more than once, he only wants the first instance of it
to remain on the list.

\section*{Input}
The first line of the input contains the positive integer $N$, denoting the number
of chores on the list. Then there are $N$ lines, each with one chore.

\section*{Output}
The output should contain the filtered list, with one chore from the list on each line.
The order matters and should be like in the input.

\section*{Scoring}
The solution will be tested on input data of varying difficulty and the data is
divided into groups as shown in the table below. The solution will then be
scored according to how many groups are solved.

\begin{tabular}{|l|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 20 & $N \leq 10$, Each line is at most $10$ characters  \\ \hline
2     & 20 & $N \leq 10^5$, Each line is at most $2$ characters \\ \hline
3     & 20 & $N \leq 10^5$, Each line is at most $10$ characters  \\ \hline
4     & 20 & $N \leq 10^3$, Each line is at most $1000$ characters  \\ \hline
5     & 20 & $N \leq 10^6$, The total number of characters in the input is at most $10^6$ \\ \hline
\end{tabular}

