\problemname{Countries}

Write a program that reads from a file, in this case named \texttt{"countries.txt"}.
An example of such a file is provided alongside the starter code.
It is guaranteed that the file will exist and is accessible by the name \texttt{"countries.txt"}.

The program should find all countries listed in the file that end with a given suffix.
Note that the comparison should be case sensitive.

\section*{Submission instructions}

\textbf{Note that we are \emph{NOT} testing any function specifically,
so your solution must handle the input and output itself!}

It is a good idea for you to break the program down into bite-sized parts
and implement each part as a function,
because it makes it easier to develop and understand the program,
but Gradescope will not test the structure of your code,
only what outputs it produces given certain inputs.

\section*{Input}
The input consists of one line containing a string $s$
representing the suffix to search for,
e.g. \texttt{"land"}.

FYI: In the test cases,
$s$ will consist of $1$ to $50$ symbols.
Each symbol in $s$ will be a digit or letter in the English alphabet.
You do not need to validate the input, or refuse other input,
this is just to inform you that you do not need to worry about other kinds of input.

\section*{Output}

% TODO: Consider changing the output format to the following:
% The first line of the output should contain the integer $N$,
% the number of countries with the given suffix.
% Then $N$ lines should follow, each one containing the name of a country ending in the given suffix.
% You should output the names in the same order they appear in the file.

Let $N$ be the number of countries with the given suffix.
Then the output should consist of $N+1$ lines.
The first $N$ lines should each one contain the name of a country ending in the given suffix.
You should output the names in the same order as they appear in the file.
Finally, the last line should contain the string\\
\texttt{\{N\} countries with suffix \{s\} in total}.
