\problemname{Shiritori}

% TODO: Get Unicode letters to render.
% Perhaps try to get the following to work:
% \usepackage[T1]{fontenc}
% \usepackage[utf8]{inputenc}

Shiritori
% (しりとり)
is a word game
in which the players are required to say a word
which begins with the final letter of the previous word.
``Shiritori'' literally means ``taking the end''.

For this problem, we will play a slightly different version of Shiritori.
Keep a list $l_1$ of valid words and another list $l_0$ of invalid words.
Whenever the user inputs a word
that does not begin with the final letter of the last valid word,
we will add it to $l_0$ and ask for another word.
If the word does begin with the final letter of the last valid word,
or if it is the first word,
we will add it to $l_1$.
The game ends when the user enters \texttt{x}.
The program should convert all input into lowercase,
so the comparison should be case-insensitive.

After the game ends,
the program should print out $l_1$ and $l_0$.
Note that the first word will never be \texttt{x}

\section*{Input}

The input consists of at least two lines, each line containing one word.

A word is a defined as series of english letters,
each word is composed of $1$ to $100$ letters.

\section*{Output}

The output consists of two lines.

The first line contains all of the words in $l_1$, seperated by a space.
It $l_1$ is empty, print an empty line.

The second line contains the all of the words in $l_0$, seperated by a space.
If $l_0$ is empty, print an empty line.

All output should be lowercase.
