\problemname{Tok Tik}
\illustration{0.3}{tik}{Image from \href{https://www.facebook.com/pages/category/Public-Figure/Toktik-388996718614860/}{facebook.com}}

Tok Tik is a new app that youngsters are absolutely raving over. There they compete
to get the most views. You have found yourself in a discussion with your friend
on who is truly the most popular Tok Tikker of all time. You decide to define
the most popular Tok Tikker of all time as the Tok Tikker who has the largest
total number of views on all their Tok Tiks. \\

You are given a list of all Tok Tiks that have been uploaded to the whole internet.
Each Tok Tik is described by what Tok Tikker uploaded it and how many views it has. \\

Determine what Tok Tikker is truly the most popular. There will always be a uniquely
determined most popular Tok Tikker.

\section*{Input}
The first line of the input contains one integer $n$ ($1 \leq n \leq 10^5$)
giving the number of Tok Tiks on the internet.

Then there are $n$ lines, one for each Tok Tik, where the $i$-th line contains
a string $s_i$ and an integer $a_i$ $(1 \leq a_i \leq 10^4)$, denoting that the
Tok Tikker $s_i$ uploaded this video and $a_i$ Tok Tikkers have viewed it.
Every string $s_i$ contains at most $20$ English lowercase letters.

\section*{Output}
Print a single line with the name of the Tok Tikker who's most popular.

\section*{Scoring}
\begin{tabular}{|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 50   & $n \leq 100$ \\ \hline
2     & 50   & No further constraints. \\ \hline
\end{tabular}

