\problemname{Indentation}

Having printed out your code, you realize that the indentation is all wrong. You need to fix this.

Write a function named \texttt{change\_indentation(text, spaces)} that takes two arguments:
\begin{itemize}
    \item \texttt{text}: a string, contains zero or more lines.
    \item \texttt{spaces}: an integer, the number of spaces to add, if positive, or remove, if negative.
\end{itemize}

The function should change the indentation for every line in the supplied string.
Following these rules it should:
\begin{enumerate}
    \item Never remove more from the front of a line than is possible without clipping the text.
    \item Never add more indentation than is possible while ensuring that no line exceeds 70 characters.
\end{enumerate}

In cases where the function needs to adjust the number of spaces
to add/remove to satisfy the given constraints,
it should add/remove the same number of spaces for every line.

\textbf{Note : please only submit your function definitions, without any code outside the functions!}


\section*{Input}
Input consists of one integer $s$, the number of spaces to indent by, where $-100 \leq s \leq 100$,
and $n$ lines, the strings that should be indented, where $0 \leq n \leq 70$.
Each string will have at most $70$ symbols.
It is guaranteed that the string will only be composed of letters from the English alphabet, spaces, and the following special characters: \texttt{, ' ? ! ( ) =}.
Furthermore, no line will contain trailing spaces.

\section*{Output}
Output consists of $n$ lines, the input strings indented by $s$ spaces.
Your output must be exactly correct, including the correct number and placement of spaces and newlines.
In particular, in each line, there should be no trailing spaces.
