\problemname{Validate name and age}

Write a program that includes two functions, \texttt{get\_name()} and \texttt{get\_age()}.

The \texttt{get\_name()} function should prompt the user: "What's your name? " If the user enters a string that does not consist of only alphabetical characters and spaces, and additionally has at least one alphabetical character, the function should print:
\begin{quote}
    Please enter a valid name.
\end{quote}
It should keep asking until the user supplies a valid name, and return the given name.

The \texttt{get\_age()} function should prompt the user: "How old are you? ". If the user inputs a string, the function should print:
\begin{quote}
    Please enter an integer.
\end{quote}
If the user inputs a number that is strictly less than $0$ or strictly greater than $125$, then the function should print:
\begin{quote}
    You seriously expect me to believe you are \{age\} years old?
\end{quote}
It should keep asking until the user supplies a valid age, and return the given age.

The program should call both these functions and print out:
\begin{quote}
    Nice to meet you \{name\}. Congratulations on your \{age\} years.
\end{quote}
where \{name\} is the value returned from \texttt{get\_name()} and \{age\} is the value returned from \texttt{get\_age()}.

\section*{Input}
Input consists of user interactions providing the name and age as prompted by the program over multiple lines.
The input consists of at most $5000$ symbols total and each one has an ASCII value in the range $32$ to $126$.

\section*{Output}
Output consists of:
\begin{enumerate}
    \item Possible prompts asking for valid input based on the criteria mentioned.
    \item A final statement greeting the user using the provided name and age.\\
    This can be on one line as above or two lines as in the samples, it does not matter.
\end{enumerate}
