\problemname{Set Operations}

Write a program that, given two files,
collects the words from each file removing all punctuations,
then computes and prints the following metrics using set operations:

\begin{itemize}
    \item Common words in both files.
    \item Words that only occur in one file but not both.
    \item Words that only appear in the first file.
\end{itemize}

For each of these, you should both print how many words there are, and the words themselves in alphabetical order.
Note: You should remove any punctuation from the start and end of each word (e.g. ``Transylvania,'' should become ``Transylvania'').

\section*{Input}
Input consists of two lines.
Both lines each contain one filename, the files that should be compared.


\section*{Output}
Output consists of three sections.
Each section starts with a specific string, they are as follows:
\begin{enumerate}
    \item First section starts with, ``\texttt{The two files have \{$n_1$\} words in common.}'',\\
where $n_1$ is the number of words the two files have in common.

    \item Second section starts with, ``\texttt{There are \{$n_2$\} words that are only in either file but not both.}''
where $n_2$ is the number of words present in one but not both files.

    \item Third section starts with, ``\texttt{There are \{$n_3$\} words that only appear in the first file.}'',
where $n_3$ is the number of words exclusive to only the first file.
\end{enumerate}

Each of these strings is then followed by the string ``\texttt{These words are as follows:}'',
unless the number of words in question is $n_i = 0$,
in which case no additional informations should be given for that particular section.
The above line should be followed by an enumeration of the relevant words;
the words that the two files have in common, that are present in only one file,
or only present in the first file, depending on the section.
In the enumeration, each word should be seperated by a comma and a space,
except the final word, which should be seperated from the previous one with an ``\texttt{ and }''.
