\problemname{The Meaning of Dictionary}

Dr. Siggi is an eccentric professor at a university in Iceland,
and he fancies himself a bit of a wordsmith.
Since 1964 he has been maintaining on his old mainframe
a dictionary that includes some words of his own making,
in addition to the wide-spread vocabulary.
However, the unthinkable has happened; his mainframe has stopped working,
and he is at risk of forgetting the meaning of all his made up words,
unless his dictionary can be salvaged and preserved for posterity.
Dr. Siggi has utilized his immense influence within the Icelandic academic sphere
to assemble the best problem solvers in Icelandic academia, and now, you are here.
Here are your instructions from Siggi.

Write a program that uses a Python dictionary to implement a dictionary.
The program repeatedly reads in a pair of inputs containing a word and its meaning,
and stores the definition of the word into the dictionary as a key-value pair.
Note: if the word is already in the dictionary, the old value should be overwritten.
After every word-definition pair, the program recives an input indicating whether there are more pairs forthcoming.
If the input is not \texttt{n} the process is repeated until it gets the input \texttt{n} after an insertion.
Finally, the program should display the words in the dictionary in alphabetical order,
along with the corresponding definitions of each.


\section*{Input}

% First, a general description of the input,
% explaining to students how to interpret
% what they are seeing in the samples below.
The lines in the input will come in threes,
where in each block of three lines,
the first line will contain a word,
the second line will contain its meaning,
and the third indicates whether there is more to come.

% Then a more precise description, leaving nothing to doubt.
Formally, the input will consist of a sequence $l = (l_1, \dots, l_{3n})$ of $3n$ lines.
For each $i$ with $1 \le i \le n$,
line $l_{3i - 2}$ will contain a word $w_i$,
line $l_{3i - 1}$ will contain its associated definition $d_i$,
and line $l_{3i}$ will contain a response $r_i$
indicating whether this is the last block or not.
So line $l_{3n}$ will consist of the single letter \texttt{n},
but for any $i < n$, line $l_{3i}$ will contain something different.

% And finally, assurances about what to expect from the test cases.
% Here we mention what we will restrict the input to in the tests,
% to clarify that they do not need to worry about input outside those restrictions.
% This does not mean their solutions should validate the input,
% or reject input that does not satisfy those restrictions.
In the tests, $n$ will be restricted to $n \le 30$.
All lines will contain only letters from the English alphabet,
as well as punctuation, spaces and possibly some numbers.
And for all $i \in \{1, \dots, n\}$,
the response $r_i$ will be either \texttt{y} or \texttt{n}.
In particular, $r_n$ will be \texttt{n}
and for all $i < n$, the response $r_i$ will be \texttt{y}.


\section*{Output}

% First, a general description of the output,
% explaining to students how to interpret
% what they are seeing in the samples below.
The output should display,
in alphabetical order,
the words from the input,
each followed by the last given definition for that word,
on a separate line,
and indented by $4$ spaces.
There should be a blank line preceding each word,
to separate the pairs.

% Then a more precise description, leaving nothing to doubt.
Formally, the output should consist of
a sequence $\lambda = (\lambda_1, \dots, \lambda_{3m})$ of $3m$ lines,
where $m$ is the number of \emph{different} words in the input.
So $1 \le m \le n$.

Let $s = (s_1, \dots, s_m)$ be a sequence of
the distinct words in the set $\{w_1, \dots, w_n\}$,
sorted in alphabetical order.
For each $i$ with $1 \le i \le m$,
line $\lambda_{3i-2}$ should be blank,
line $\lambda_{3i-1}$ should contain the word $s_i$,
and line $\lambda_{3i}$ should start wit $4$ spaces,
followed by the definition of the word $s_i$
that was given the last time the word $s_i$ appeared in the input.
To be precise, let $j = \max\{k\mid w_k = s_i\}$.
Then line $\lambda_{3i}$ should contain the definition $d_j$,
preceded by $4$ spaces.
