\problemname{Ages}

Write a program that:
\begin{enumerate}
    \item Allows the user to input the names and ages of several persons.
    \item Determines who the oldest and youngest persons are.
    \item Shows the median and average ages, rounded to the $2$nd decimal.
    \begin{itemize}
        \item
        If there's an even number of people,
        then the median is the average of the two central values in a sorted list.
    \end{itemize}
\end{enumerate}

The program should be robust enough to handle invalid input
when the user fails to type an integer when one is expected.

\section*{Input}
First, the program should prompt the user for an integer $n$, the number of people.\\
If an integer is not input the program should output the following:

\texttt{\{$n$\} is not an integer. Please try again.}\\
until the user inputs an integer.

The following then repeats $n$ times, for each $i$ satisfying $1 \le i \le n$:
\begin{itemize}
    \item The program prompts the user for the name $N_i$ of person $p_i$.

    \item
    The program prompts the user for the age $H_i$ of person $p_i$, where $1 \leq H_i \leq 100$.\\
    If an integer is not input the program should output the following:

    \texttt{\{$H_i$\} is not an integer. Please try again.}\\
    and prompt the user again.
\end{itemize}

\section*{Output}
After any error messages have been displayed as a response to erroneous input,
the output should conclude with the following four lines:
\begin{itemize}
    \item
    \texttt{The oldest person is \{$N_o$\} who is \{$H_o$\} years old}\\
    where $N_o$ and $H_o$ are the name and age of the oldest person.

    \item
    \texttt{The youngest person is \{$N_y$\} who is \{$H_y$\} years old}\\
    where $N_y$ and $H_y$ are the name and age of the youngest person.

    \item
    \texttt{The median age is \{$\mu_{1/2}$\}}\\
    where $\mu_{1/2}$ is the median age, and should be rounded to the 2nd decimal.

    \item
    \texttt{The average age is \{$\mu$\}}\\
    where $\mu$ is the average age, and should be rounded to the 2nd decimal.
\end{itemize}
