\problemname{Comrade Computer Operator}
\illustration{0.3}{nuclear}{Radioactive!}

Your nation's prestigious reputation is being tarnished by the evil foreign
media due to a slight mishap in one of its nucelar power plants.
To prevent this from happening again, the wise leaders of your nation have
given you the task to create a computer program that controls reactor temperature.
At regular intervals, the temperature of the water in the reactor is measured.
The last two measurements are given to the program, which then decides what should
be done with the control rods in order to maintain an optimum operating temperature
of $300^\circ C$. The control logic is as follows:

\begin{itemize}
    \item If the current temperature is below $300^\circ C$ and the temperature is not rising then raise the control rods to increase temperature.
    \item If the current temperature is below $300^\circ C$ but the temperature is rising then keep the control rods where they are.
    \item If the current temperature is exactly $300^\circ C$ then keep the control rods where they are.
    \item If the current temperature is above $300^\circ C$ and the temperature is not falling then lower the control rods to reduce temperature.
    \item If the current temperature is above $300^\circ C$ but the temperature is falling then keep the control rods where they are.
    \item If the current temperature is $350^\circ C$ or higher then initiate emergency shutdown procedures.
\end{itemize}

Can you write the program and save your nation's reputation?

\section*{Input}
The input consists of two lines.
The first line contains one integer $a$, the current temperature, where $0 \leq a \leq 400$.
The second line contains one integer $b$, the previous temperature, where $0 \leq b \leq 349$.

\section*{Output}
Depending on the pair of measurements, output \texttt{raise}, \texttt{keep}, \texttt{lower} or \texttt{shutdown}.
