\problemname{Clock}

The clocks at Reykjavík University heve begun ticking backwards and Ingi from facilities, having heard of your previous tales, comes asking for help fixing the situation.

\textbf{The main file, which handles input and output, is already provided. -
Please only submit your class definition, without any code outside the class!}

Implement a class called \texttt{Clock} with the following attributes:

\begin{itemize}
    \item An \texttt{\_\_init\_\_()} method with three parameters: hours, minutes, seconds with default values 0.
    \item Three instance variables to store the hours, minutes and seconds.
    \item A method called \texttt{str\_update()}. 
    It takes as an argument a string of the form hh:mm:ss and updates the three instances variables.
    \item A \texttt{\_\_str\_\_()} method for responding to the \texttt{print} function. It should write out: \texttt{"\{\} hours, \{\} minutes and \{\} seconds."}
    \item A method called \texttt{add\_clocks()}.
    It takes another clock object as a parameter, adds the two clocks and returns a new clock instance.
    In this method, you need to add the respective values of the two clocks together and remember the resulting hours, minutes and seconds.
    Remember that the sum of seconds cannot exceed 60, in which case there is a carry over to the minutes values.
    Same for minutes, it cannot exceed 60 and carries over to hours.
    For hours, the summed values cannot exceed 24.
    If hours is exceeded, we ignore it and start from zero.
    Try to use the \texttt{divmod()} built-in Python function in your implementation.
\end{itemize}

The file submitted should be named: \texttt{clock.py}


\section*{Example}
Example use of class:
\begin{verbatim}
clock1 = Clock()
clock2 = Clock(8, 30)
print(clock1)
print(clock2)
clock1.str_update("03:21:34")
clock2.str_update("05:45:52")
print(clock1)
print(clock2)
clock3 = clock1.add_clocks(clock2)
print(clock3)
\end{verbatim}
    

Corresponding output:
\begin{verbatim}
0 hours, 0 minutes and 0 seconds.
8 hours, 30 minutes and 0 seconds.
3 hours, 21 minutes and 34 seconds.
5 hours, 45 minutes and 52 seconds.
9 hours, 7 minutes and 26 seconds.
\end{verbatim}
