\problemname{Sound of Anagrams}

The underground rap scene at Reykjavik University is brutal, only the best survive.
However, good music is not enough, you must also have a banger title.
Nowadays, anagrams are in style,
so Diddi from the law department wants your help to create a program
that can determine if two sentences are anagrams.

A word is an anagram of another word
if the characters in one of the words can be rearranged to form the other word.
We can extend this definition to sentences
if we allow spaces between words, and ignore punctuation.

Write a program that accepts as input 2 sentences.
The program should then convert the input strings into a dictionary,
where the key is a letter in the sentence,
and the value is the count of the character in the sentence.
Do not add punctuation or spaces into the dictionary
(HINT: \texttt{import string.punctuation}).

The program should report whether the two sentences are anagrams of each other.

Note: The sentences should be compared in a case-insensitive manner,
so the program should not differentiate between upper case and lower case letters.


\section*{Input}

The input will consist of $2$ lines,
containing one sentence each, $S_1$ and $S_2$.
In the tests, the length of each $S_i$ will be restricted to $|S_i| \leq 70$.


\section*{Output}

The output should consist of one line.
If $S_1$ is an anagram of $S_2$, the program should print out:
\begin{itemize}
    \item
    \texttt{\{$S_1$\} is an anagram of \{$S_2$\}.}
\end{itemize}
Otherwise, the program should print out:
\begin{itemize}
    \item
    \texttt{\{$S_1$\} is not an anagram of \{$S_2$\}.}
\end{itemize}

