\problemname{Barcelona}
\illustration{0.3}{baggage_claim}{Image from \href{https://www.flickr.com/photos/sandiegointernationalairport/4860291021/}{flickr.com}}

Arnar, Benni and Unnar were at the airport in Barcelona on their way to a competitive programming training camp.
When the plane had landed they exited and went to the baggage claim.
When they arrived there was no baggage on the conveyor belts.
After a few minutes the baggage started trickling in.
When Benni noticed this he loudly proclaimed
``My bag's first! No, it's second first! No...\ it's fourth first. No wait...''

Given a list of bags and a number denoting Benni's bag,
can you help Benni find how first his bag is?

\section*{Input}
First there is a line with two integers $n$ and $k$,
the number of bags and Benni's bag.
It will always hold that $1 \leq n \leq 10^5$ and $-10^9 \leq k \leq 10^9$.
Next there is a line with $n$ integers separated by spaces, $a_1, a_2, \dotsc, a_n$.
For each $1 \leq i \leq n$ it holds that $-10^9 \leq a_i \leq 10^9$.
No two bags are given by the same number and Benni's bag always appears in the list.

\section*{Output}
Print a single line.
If Benni's bag is first print \texttt{fyrst},
if it's the second print \texttt{naestfyrst}.
Otherwise print a single number denoting how first it is
followed by the word \texttt{fyrst} after the number.

\section*{Scoring}
\begin{tabular}{|l|l|l|l|}
\hline
Group & Points & Constraints \\ \hline
1     & 10  & $1 \leq n \leq 100$ \\ \hline
2     & 90  & No further constraints \\ \hline
\end{tabular}
